The title

### 2020-11-23 scripts/draft_play.Rmd
Peer Review

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "Makayla Whitney"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "University of Oregon"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

@@

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

>>>>

---
title             : "The title"
shorttitle        : "Title"
author: 
  - name          : "Makayla Whitney"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
    role:
      - Writing - Review & Editing
affiliation:
  - id            : "1"
    institution   : "University of Oregon"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

@@

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---
